### 2023-03-02 intro.tex

To recover further, we might choose to also ignore the bidirectional type system's demand that the guard be confirmed to be a boolean expression 
(because the type of \li{f(y)} is also not well-defined) 
and continue into its branches, observing that they have inconsistent types, \li{Int} and \li{Bool}. 
There are several ways to localize this error. 
One approach would be to assume, arbitrarily, that one branch is correct, localizing the error to the other branch. 
Heuristics have been developed to help make this choice less arbitrary, e.g. 
by observing recent editing history \todo{cite}, 
or training a machine learning model \todo{cite}. 
The other approach, which we take in Hazel, is to localize the inconsistency to the conditional expression itself, reporting that the problem is that the branch types differ, as indicated in
the screenshot in \autoref{fig:hazel-intro}. When the cursor is on the conditional expression, the Hazel type inspector---a status bar that reports typing information, including type error messages, about the term at the cursor \cite{hannah1}---shows the following error:

@@

>>>>

To recover further, we might choose to also ignore the bidirectional type system's demand that the guard be confirmed to be a boolean expression 
(because the type of \li{f(y)} is also not well-defined) 
and continue into its branches, observing that they have inconsistent types, \li{Int} and \li{Bool}. 
There are several ways to localize this error. 
One approach would be to assume, arbitrarily, that one branch is correct, localizing the error to the other branch. 
Heuristics have been developed to help make this choice less arbitrary, e.g. 
by observing recent editing history \todo{cite}, 
or training a machine learning model \todo{cite}. 
The other approach, which Hazel takes, is to localize the inconsistency to the conditional expression itself, reporting that the problem is that the branch types differ, as indicated in
the screenshot in \autoref{fig:hazel-intro}. When the cursor is on the conditional expression, the Hazel type inspector---a status bar that reports typing information, including type error messages, about the term at the cursor \cite{hannah1}---shows the following error:

@@

let x : ? = ? in 
if x then x(x + 1) else
